Puck Predictions: Unraveling the NHL Game Forecasting Riddle

### 2024-03-28 Latex/draft.tex
worked on MCMC latex

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts,hyperref, enumitem, tikz}

@@

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts,hyperref, enumitem, tikz}
\usepackage{algorithm}
\usepackage{algpseudocode}

@@

To simulate hockey games, we setup a Markov Chain where the states are a tuple of three consecutive
events that occurred. For example, if the home team won a faceoff, the home team lost the puck, and 
then the away team shot the puck and missed, the markov chain would look like figure \ref{fig:markov_chain_sample}.
The probabilities of transitioning from one triple-state to another triple-state is calculated by:
\begin{align*}
    P(s_{t+1} = (B,C,D) \;|\; s_t = (A,B,C)) &= P(D \;|\; (A,B,C)) \\
    &= \frac{\{ \text{\# of times (A,B,C,D) happend}\}}{\{ \text{\# of times (A,B,C) happened}\}} \\
\end{align*}
Where $A,B,C,D$ are events that can occur in a game, and the tuple (A,B,C,D) represents that "A then 
B then C then D" happend right after eachother in a game.

To simulate a game, we performed this monte carlo algorithm:

\begin{algorithm}
\caption{Simulation Algorithm}
\begin{algorithmic}[1]
\State $\text{time\_remaining} \gets 3600$
\State $s0 \gets "\#"$
\State $s1 \gets "\#"$
\State $s2 \gets "\#"$

\While{$\text{time\_remaining} > 0$}
    \State $\text{next\_state} \gets \text{sample from } \text{MC(curr\_state)}$
    \State $s0 \gets s1$
    \State $s1 \gets s2$
    \State $s2 \gets \text{next\_state}$

    \State $\text{event\_time} \gets \text{sample from } \text{KDE\_times()}$
    \State $\text{time\_remainting} \gets \text{time\_remainting} - \text{event\_time}$
\EndWhile
\end{algorithmic}
\end{algorithm}

% add the image images/markov_chain_sample.png
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.8\textwidth]{images/markov_chain_sample.png}
    \caption{Sample Markov Chain for the current state (home team won faceoff, 
    home team lost puck, away team missed shot) with the probabilities of the next event 
    sorted from highest to lowest}
    \label{fig:markov_chain_sample}
\end{figure}
